swaps

### 2021-08-13 R/climber_swaps.Rmd
start some sort of sensitivity analysis of total ranking based on event

### How unstable are the medalists in their positions?

>>>>

### How volatile are the scores depending on the event?

```{r}
# swaps 2 scores
swap_cons <- function(n, n1, n2) {
  if (n == n1) {
    return(n2)
  } else if (n == n2) {
    return(n1)
  } else {
    return(n)
  }
}
```

below is a table summarizing the results for all consecutive ranking swaps in each event, holding the other 2 events constant.

```{r, echo = FALSE}
mens_swaps_all <- 
  mens_swaps12 %>% 
  filter(swap == "original") %>%
  group_by(climber) %>%
  mutate(speed_12 = swap_cons(speed, 1, 2)
         , speed_23 = swap_cons(speed, 2, 3)
         , speed_34 = swap_cons(speed, 3, 4)
         , speed_45 = swap_cons(speed, 4, 5)
         , speed_56 = swap_cons(speed, 5, 6)
         , speed_67 = swap_cons(speed, 6, 7)
         ) %>%
  mutate(bould_12 = swap_cons(bould, 1, 2)
         , bould_23 = swap_cons(bould, 2, 3)
         , bould_34 = swap_cons(bould, 3, 4)
         , bould_45 = swap_cons(bould, 4, 5)
         , bould_56 = swap_cons(bould, 5, 6)
         , bould_67 = swap_cons(bould, 6, 7)
         ) %>%
  mutate(lead_12 = swap_cons(lead, 1, 2)
         , lead_23 = swap_cons(lead, 2, 3)
         , lead_34 = swap_cons(lead, 3, 4)
         , lead_45 = swap_cons(lead, 4, 5)
         , lead_56 = swap_cons(lead, 5, 6)
         , lead_67 = swap_cons(lead, 6, 7)
         ) %>%
  ungroup() %>%
  select(-c(swap, total_rank, total)) %>%
  pivot_longer(speed:lead_67) %>%
  mutate(event = sub("_.*", "", name)
         , swap = ifelse(name %in% c("speed", "bould", "lead"), "original", name)
         ) %>%
  select(-name) %>%
  pivot_wider(names_from = event, values_from = value) %>%
  group_by(climber) %>%
  mutate(speed = ifelse(is.na(speed), speed[swap == "original"], speed)
         , bould = ifelse(is.na(bould), bould[swap == "original"], bould)
         , lead = ifelse(is.na(lead), lead[swap == "original"], lead)
         ) %>%
  ungroup() %>%
  mutate(total_score = speed*bould*lead) %>%
  group_by(swap) %>%
  mutate(total_rank = rank(total_score)) %>%
  ungroup() %>%
  arrange(swap, total_rank)  %>%
  separate(swap, into = c("swap", "position"), sep = "_")

mens_swaps_all %>% knitr::kable()
```
